Manuscript progress report

### 2024-01-19 Docs/manuscript.Rmd
change spline basis for GFOSR model

# model
t1 <- Sys.time()
fit_gen_fosr <- bam(Y ~ s(t, bs="cc", k=20) + 
                        s(t, bs="cc", k=20, by = yl),
                   family = binomial, data=df_pred_tr, 
                   method = "fREML",
                   discrete = TRUE)
t2 <- Sys.time()
t2-t1

@@

t1 <- Sys.time()
for(w in 1:4){
  # model fit
  # predictor (training set)
  y_obs_max <- train_df %>% filter(window==w) %>% arrange(desc(t)) %>%
    group_by(id) %>%
    slice(L) %>% select(id, Y) %>% rename(yl = Y)
  # outcome (training set)
  df_pred_tr <- train_df %>% filter(window > w) %>%
    left_join(y_obs_max, by = "id") %>% 
    mutate_at(vars(Y, yl), as.factor)
  # model 
  fit_gen_fosr <- bam(Y ~ s(t, bs="cc", k=20) + 
                        s(t, bs="cc", k=20, by = yl),
                   family = binomial, data=df_pred_tr, 
                   method = "fREML",
                   discrete = TRUE)

@@

```{r}
t1 <- Sys.time()
for(w in 1:4){
  # model fit
  # predictor (training set)
  y_obs_max <- train_df %>% filter(window==w) %>% group_by(id) %>%
    slice_max(t, n=5) %>% select(id, Y, sind) %>%
    mutate(name = sind-min(sind)+1) %>%
    pivot_wider(id_cols = id, values_from = Y, names_from = "name", names_prefix = "yl")
  # outcome (training set)
  df_pred_tr <- train_df %>% filter(window > w) %>%
    left_join(y_obs_max, by = "id") %>% 
    mutate_at(vars(Y, starts_with("yl")), as.factor) 
  fit_gen_fosr <- bam(Y ~ s(t, bs="cc", k=20) + 
                        s(t, bs="cc", k=20, by = yl5)+
                        s(t, bs="cc", k=20, by = yl4)+
                        s(t, bs="cc", k=20, by = yl3)+
                        s(t, bs="cc", k=20, by = yl2)+
                        s(t, bs="cc", k=20, by = yl1),
                   family = binomial, data=df_pred_tr, 
                   method = "fREML",
                   discrete = TRUE)

@@

```{r}
data.frame(Window = c("(0.2,0.4]", "(0.4,0.6]", "(0.6,0.8]", "(0.8, 1.0]"),
           tb_ies_l1, tb_ies_l5, check.names = F) %>%
  kable(digits = 3, caption = "Integrated squared error", booktabs = T) %>%
  kable_styling(full_width = F) %>% 
  add_header_above(c(" "=1, "L = 1" = 4, "L = 5" = 4)) %>%
  add_header_above(c(" "= 1, "Observation track" = 8))
```

>>>>

# model
t1 <- Sys.time()
fit_gen_fosr <- bam(Y ~ s(t, bs="cr", k=20) + 
                        s(t, bs="cr", k=20, by = yl),
                   family = binomial, data=df_pred_tr, 
                   method = "fREML",
                   discrete = TRUE)
t2 <- Sys.time()
t2-t1

@@

t1 <- Sys.time()
for(w in 1:4){
  # model fit
  # predictor (training set)
  y_obs_max <- train_df %>% filter(window==w) %>% arrange(desc(t)) %>%
    group_by(id) %>%
    slice(L) %>% select(id, Y) %>% rename(yl = Y)
  # outcome (training set)
  df_pred_tr <- train_df %>% filter(window > w) %>%
    left_join(y_obs_max, by = "id") %>% 
    mutate_at(vars(Y, yl), as.factor)
  # model 
  fit_gen_fosr <- bam(Y ~ s(t, bs="cr", k=20) + 
                        s(t, bs="cr", k=20, by = yl),
                   family = binomial, data=df_pred_tr, 
                   method = "fREML",
                   discrete = TRUE)

@@

```{r}
t1 <- Sys.time()
for(w in 1:4){
  # model fit
  # predictor (training set)
  y_obs_max <- train_df %>% filter(window==w) %>% group_by(id) %>%
    slice_max(t, n=5) %>% select(id, Y, sind) %>%
    mutate(name = sind-min(sind)+1) %>%
    pivot_wider(id_cols = id, values_from = Y, names_from = "name", names_prefix = "yl")
  # outcome (training set)
  df_pred_tr <- train_df %>% filter(window > w) %>%
    left_join(y_obs_max, by = "id") %>% 
    mutate_at(vars(Y, starts_with("yl")), as.factor) 
  fit_gen_fosr <- bam(Y ~ s(t, bs="cr", k=20) + 
                        s(t, bs="cr", k=20, by = yl5)+
                        s(t, bs="cr", k=20, by = yl4)+
                        s(t, bs="cr", k=20, by = yl3)+
                        s(t, bs="cr", k=20, by = yl2)+
                        s(t, bs="cr", k=20, by = yl1),
                   family = binomial, data=df_pred_tr, 
                   method = "fREML",
                   discrete = TRUE)

@@

```{r}
data.frame(Window = c("(0.2,0.4]", "(0.4,0.6]", "(0.6,0.8]", "(0.8, 1.0]"),
           tb_ies_l1, tb_ies_l5, check.names = F) %>%
  kable(digits = 3, caption = "Integrated squared error", booktabs = T,
        table.attr = "style = \"color: black;\"") %>%
  kable_styling(full_width = F) %>% 
  add_header_above(c(" "=1, "L = 1" = 4, "L = 5" = 4)) %>%
  add_header_above(c(" "= 1, "Observation track" = 8))
```
